Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-29 reply_2/cover_letter.tex
Add reference to 'diffs' file in cover letter

@@

>>>>

We have made the requested changes and have tried to address each of
the points raised by the referees.

@@

Finally, to make it easier to see the changes in this version of the
paper, we have attached a second copy of the paper that highlights the
specific differences from the previous version. (Blue text has been
added since the last version; red indicates deleted text.)

Thanks again for giving us this opportunity.
